### 2024-05-19 fantasy-football.qmd
20240519 - more additions and edits

- Quarterback (QB)
- Running Back (RB), also called halfback or tailback
- Fullback (FB)
- Wide Receiver (WR)
- Tight End (TE)
- Offensive Line (OL)
    - Center (C)
    - Offensive Guard (OG)
    - Offensive Tackle (OT)

Quarterbacks are the most important player on the offense.
They help lead the team down the field.
Quarterbacks receive the ball from the Center at the beginning of the play, and they can either hand the ball off (typically to a Running Back or Fullback), pass the ball (typically to a Wide Receiver or Tight End), or run the ball.

Running Backs take a hand-off from the Quarterback to execute a running play.
They may also catch short passes from the Quarterback or help protect (i.e., block for) the Quarterback from the defensive players who are trying to tackle the Quarterback.

Wide Receivers catch passes from the Quarterback to execute a passing play.
On running plays, they provide protection for the player running the ball (e.g., the running back) so they can get as far as possible without being tackled.

Tight Ends block for running and passing plays, and they catch passes from the Quarterback.

The players on the Offensive Line block for running and passing plays.
On passing plays, they provide protection for the Quarterback so the Quarterback has time to pass the ball without being tackled.
On running plays, they provide protection for the player running the ball (e.g., the running back) so they can get as far as possible without being tackled.

@@

- Defensive Line (DL)
    - Defensive End (DE)
    - Defensive Tackle (DT)
- Linebacker (LB)
    - Middle Linebacker (MLB)
    - Outside Linebacker (OLB)
- Defensive Back (DB)
    - Cornerback (CB)
    - Safety (S)
        - Free Safety (FS)
        - Strong Safety (SS)

@@

@@

A "flex position" is a flexible position that can involve a player from various positions: e.g., a Running Back, Wide Receiver, or Tight End.
In fantasy football, Fullbacks are classified as Running Backs because they both run the ball.

>>>>

- Quarterback (QB)
- Running Back (RB)
    - Halfback or Tailback
    - Fullback (FB)
- Wide Receiver (WR)
- Tight End (TE)
- Offensive Line (OL)
    - Center (C)
    - Offensive Guard (OG)
    - Offensive Tackle (OT)

Quarterbacks are the most important player on the offense.
They help lead the team down the field.
Quarterbacks receive the ball from the Center at the beginning of the play, and they can either hand the ball off (typically to a Running Back or Fullback), pass the ball (typically to a Wide Receiver or Tight End), or run the ball.
Quarterbacks tend to have a strong arm for throwing the ball far and accurately.

Running Backs take a hand-off from the Quarterback to execute a running play.
They may also catch short passes from the Quarterback or help protect (i.e., block for) the Quarterback from the defensive players who are trying to tackle the Quarterback.
Halfbacks or Tailbacks tend to be quick and agile.
Fullbacks tend to be strong and powerful.

Wide Receivers catch passes from the Quarterback to execute a passing play.
On running plays, they provide protection for the player running the ball (e.g., the Running Back) so the ball carrier can get as far as possible without being tackled.
Wide receivers tend to be tall, fast, have good hands (can catch the ball well), and can jump high.

Tight Ends block for running and passing plays, and they catch passes from the Quarterback.
Tight ends tend to be strong and have good hands.

The players on the Offensive Line block for running and passing plays.
On passing plays, they provide protection for the Quarterback so the Quarterback has time to pass the ball without being tackled.
On running plays, they provide protection for the player running the ball (e.g., the Running Back) so the ball carrier can get as far as possible without being tackled.
Players on the Offensive Line tend to be large so they can provide adequate protection for the Quarterback and Running Back.

@@

- Defensive Line (DL)
    - Defensive End (DE)
    - Defensive Tackle (DT)
- Linebacker (LB)
    - Middle (or Inside) Linebacker (MLB)
    - Outside Linebacker (OLB)
- "The Secondary" / Defensive Back (DB)
    - Cornerback (CB)
    - Safety (S)
        - Free Safety (FS)
        - Strong Safety (SS)

The players on the defense attempt to tackle the offensive players for as short of gains as possible and attempt to prevent completed passes.

On passing plays, the players on the Defensive Line try to apply pressure to the Quarterback and try to sack them.
On rushing plays, the players on the Defensive Line try to tackle the ball carrier.
Players on the Defensive Line tend to be large yet quick so they can apply pressure to the Quarterback.

Linebackers are versatile in that, on a given play, they may attempt to a) "blitz" to sack the Quarterback, b) stop the Running Back, or c) prevent a completed pass.
Linebackers tend to be strong yet agile.

Defensive Backs are specialist pass defenders.
The main role of Cornerbacks is to cover the Wide Receivers.
Safeties serve as the last line of defense for longer passes.
Defensive Backs tend to be quick and agile.

@@

On a field goal attempt, the Long Snapper snaps the ball to the Holder, who holds the ball for the Kicker.
The Kicker attempts field goals and, during kickoffs, kicks the ball to the opposing team.
During kickoffs, the Kick Returner catches the kicked ball and returns it for as many yards as possible.
During a punt play, the Long Snapper snaps the ball to the Punter who kicks (i.e., punts) the ball to the opposing team.
The Punt Returner catches the punted ball and returns it for as many yards as possible.

@@

A "flex position" is a flexible position that can involve a player from various positions: e.g., a Running Back, Wide Receiver, or Tight End.
